Secure Composition of Robust and Optimising Compilers

### 2023-07-06 popl/main.tex
Rework up to section 5

Given a partial program $\progvar$, i.e., a program with free variables, the execution of $\progvar$ would get stuck due to the lack of definitions.
%As described earlier, partial programs cannot be executed \MP{not true anymore, need to define the notion of partial programs} , because they lack definitions and, thus, get stuck.
To remedy this, {\em linking} takes two partial programs $\progvar[_{1}],\progvar[_{2}]$ and produces a new whole program $\link{\progvar[_{1}]}{\progvar[_{2}]}$.
%Note that linking is not defined on programs, but merely on their syntactic descriptions, since programs contain dynamic state.\MP{ not terminology i really want to use, nor is defined}
As typically done in secure compilation~\cite{abate2019jour}, \MP{others do this too, parametricity results e.g.} this paper assumes that programs are the result of linking a {\em context} ($\ctx$) and a {\em component} ($\comp$).
% \MP{just introduce the notion of contexts}
%       MK: why only contexts?
%The component part of a whole program is the main object of interest and thus a known syntactic description.
The context is usually arbitrary\footnote{Up to, e.g., provoking link failure.} and thus has the role of an {\em attacker} that can interact with the component by means of whatever features the programming language has.
The semantics of the programming language is expected to differentiate between the component and the context.
%\MP{and say the semantics is expected (passive, hah) to differentiate between prg and ctx}
%%                                         -> why passive?
So, the context interacts in some way with the component and this interaction models an attacker.
With this, \Thmref{def:propsat} can be extended as follows.
For \bul{programs $\progvar$ to robustly satisfy a property $\pi$}, take an \iul{attacker $\contextvar$ and link it with $\progvar$}, \oul{the result of which must satisfy $\pi$}.
%The following definition extends on \Thmref{def:propsat} to cover property satisfaction under the presence of an (active, with respect to the semantics of the programming language) attacker: %, which is known as {\em robust satisfaction}:
%\MPin{missing: the context is an attacker! now, unlike before, we security property satisfaction with a clear active attacker}

@@

\section{Example Properties and their Monitors\pages{3}}\label{sec:compprop}

This section introduces a trace model (\Cref{subsec:propdefs}) that is used to define some example properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{scct}).
These properties are of practical importance and also of interest in the case study (\Cref{sec:casestud:defs,sec:casestud:rtp}) this paper presents.
The study uses monitors, which are able to check wether a trace admits a property or not.
The use of monitors is because they have some structure useful for inductive proofs, whereas traces lack this structure, thus making proofs difficult.
So, this section also presents monitors for each of the defined properties (\Cref{subsec:monitors}) and introduces monitor-based satisfaction.
Finally, for each property, it is shown that monitor-based satisfaction implies property satisfaction.

\subsection{Specification Trace Model}\label{subsec:propdefs}

@@

The specification trace model has events that carry different meta-information, such as security- and control--tags.
Security tags describe wether an event contains sensitive information ($\lock$) or not ($\unlock$).
Control tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
%Even though this could be used for blame~\cite{patrignani2023blame}, this is not what this paper is concerned about.
Now, pre--events describe the actual kind of event that happened.
One such kind is the allocation event ($\ev{Alloc\ \loc\ n}$) that happens whenever a program claims $n$ cells of memory and stores them at address $\loc$.
Likewise, deallocation ($\ev{Dealloc\ \loc}$) announces that the object at location $\loc$ is freed.
These two events alone allow already a partial description of \gls{tms} by requiring that e.g. there is only one deallocation event that carries a location $\loc$.
To be able to express \gls{sms}, there is also an event to describe reads from and writes to memory ($\ev{Use\ \loc\ n}$).
For cryptographic code, there is a general guideline that secrets must not be visible on a trace.
Moreover, an instruction whose timing is data--dependent must not have a secret as an operand.
Typical operations with data--dependent timing are branches and certain binary operations, such as division.
Both operations are also modelled in the specification trace model ($\ev{Branch\ n}$ and $\ev{Binop\ n}$).
Lastly, events are either the empty event ($\emptyevent$), a program crash ($\lightning$), or a tuple consisting of a pre-event, a control--tag, and a security--tag.

\gls{tms} requires that pointers are freed exactly once and that no use happens after a free.

\begin{definition}[\glsfirst{tms}]\label{def:trace:tmsdef}
  A trace $\trace$ is temporal memory safe ($\trace\in\tmssafe$) iff $\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Dealloc\ \loc;\sandboxtag';\securitytag'}$, $\ev{Use\ \loc\ n;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Alloc\ \loc\ m;\sandboxtag';\securitytag'}$ and $\ev{Dealloc\ \loc;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Use\ \loc\ n;\sandboxtag';\securitytag'}$.
\end{definition}

\gls{sms} disregards out of bounds accesses.

\begin{definition}[\glsfirst{sms}]\label{def:trace:smsdef}
  A trace $\trace$ is spatial memory safe ($\trace\in\smssafe$) iff given $\ev{Alloc\ \loc\ m;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ n;\sandboxtag';\securitytag'}$, then $n<m$.
\end{definition}

Full \gls{ms} is then described as the conjunction of \Cref{def:trace:tmsdef,def:trace:smsdef}.

\begin{definition}[\glsfirst{ms}]\label{def:trace:msdef}
  A trace $\trace$ is memory safe ($\trace\in\mssafe$) iff $\trace\in\tmssafe$ and $\trace\in\smssafe$.
\end{definition}

A variant of the \gls{cct} security property is defined.
Generally, one cannot define \gls{cct} just as trace-property without, e.g., performing a self-composition of a program.
That is why this paper adopts a stricter variant of \gls{cct}, called \gls{scct}, that enforces common policies to ensure code is \gls{cct}.
For example, one must not branch on secrets or perform binary operations, such as division, on secrets whose timing is data-dependent.
Even stronger, \gls{scct} disregards any secrets leaked on a trace.
To define the property, a function on traces is needed that strips all events with a $\lock$-tag: $\downarrow_{\lock}(\cdot)$.

\begin{definition}[\glsfirst{scct}]
  A trace $\trace$ is strictly cryptographic constant time ($\trace\in\scctsafe$) iff $\trace=\downarrow_{\lock}\left(\trace\right)$.
\end{definition}

\subsection{Monitors and Trace Agreements}\label{subsec:monitors}

This subsection presents monitors for properties \gls{tms}, \gls{sms}, \gls{ms}, and \gls{scct}.
Each monitor $\monitor$ has its own accompanying trace model that abstracts over the most general trace model.
%This is because monitors should only be concerned with property-relevant information.
Traces of the accompanying trace model are written as $\abstrace$ and $\monitorcheck{\monitor}{\monitor[']}{\abstrace}$ is the notation for the semantics of a monitor.
The empty monitor is denoted as $\emptyset$.
For each model of a monitor, an agreement relation $\traceagree{\pi}{\trace}{\abstrace}$ is defined that relates monitor specific traces with most general traces.
The notation $\traceagree[]{\pi}{\event}{\absevent}$ is used to relate just events and the star version of it is defined similarily to \Cref{fig:starstep:and:nstep}.
With this, first, monitor satisfaction is defined and then the individual monitors.
Finally, for every monitor, it is shown that monitor satisfaction implies trace property satisfaction.

\begin{definition}[Monitor Satisfaction]\label{def:monsat}
  A given trace $\trace$ monitor-satisfies a property $\pi$ ($\monsafe{\trace}{\pi}$) iff %
  there exists $\abstrace,\monitor$ such that $\traceagree{\pi}{\trace}{\abstrace}$ and $\monitorcheck{\emptyset}{\monitor}{\abstrace}$.
  \Coqed
\end{definition}

\paragraph{Monitor for \glsfirst{tms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{alloced}:L,\text{freed}:L\right\} \hspace{0.33cm}%
    \emptyset:=\ \left\{\text{alloced}:\emptyset,\text{freed}:\emptyset\right\}\\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc \mid \absev{Dealloc\ }\loc \mid \absev{Use\ }\loc \mid \absterm\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
  \typerule{tms-uninteresting}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
  }{tms-uninteresting}
  %
  \typerule{tms-abort}{
  }{
    \monitorcheck[]{\tmsmonitor}{\emptyset}{\absterm}
  }{tms-abort}
  %
  \typerule{tms-use}{
    \loc\in\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    \loc\notin\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\cup\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    \loc\in\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\setminus\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\cup\left\{\loc\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc}
  }{tms-dealloc}
\end{center}
\begin{center}
  \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ with respect to \gls{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc}
  }{tms-alloc-authentic}
  %
  \typerule{tms-dealloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{tms-dealloc-authentic}
  %
  \typerule{tms-use-authentic}{
  }{
    \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
  }{tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{tms-branch-authentic}
  %
  \typerule{tms-binop-authentic}{
  }{
    \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{tms-binop-authentic}
  %
  \typerule{tms-empty-authentic}{
  }{
    \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{tms-empty-authentic}
  %
  \typerule{tms-abort-authentic}{
  }{
    \tmstraceagree[]{\lightning}{\absterm}
  }{tms-abort-authentic}
\end{center}

The state of the monitor is a record containing two sets that keep track of allocated and freed locations.
The monitor runs on a modified trace semantics with more abstract $\absev{Alloc\ }\loc$,$\absev{Dealloc\ }\loc$,$\absev{Use\ }\loc$, and $\absterm$ events, which represent {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.
\Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
\Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and depending on the witnessed action, extend the internal state of the monitor.
The trace agreement is entirely straightforward.

\begin{lemma}[Traces with Monitor Satisfaction are $\tmssafe$]\label{lem:mon:tmsafe}
  If $\montmssafe{\trace}$, then $\trace\in\tmssafe$.\Coqed
\end{lemma}

\paragraph{Monitor for \glsfirst{sms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\smsmonitor:=\ L\times\mb{N}\hspace{0.33cm}&
    \mi{(Abstract\ Events)}~\absevent\bnfdef\ \absev{\varepsilon} \mid \absev{Alloc\ }\loc\ n \mid \absev{Dealloc\ }\loc \mid \absev{Use\ }\loc\ n \\
  \end{aligned}
\end{gather*}
\MKin{do we really need $\absev{Dealloc}$?}
\begin{center}
  \judgbox{\monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\absevent}}{,,Monitor $\smsmonitor$ steps to $\smsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
  \typerule{sms-uninteresting}{
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor}{\absev{\emptyevent}}
  }{sms-uninteresting}
  %
  \typerule{sms-abort}{
  }{
    \monitorcheck[]{\smsmonitor}{\emptyset}{\absterm}
  }{sms-abort}
  %
  \typerule{sms-use}{
    (\loc,m)\in\smsmonitor &
    n<m
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor}{\absev{Use\ }\loc\ n}
  }{sms-use}
  %
  \typerule{sms-alloc}{
    \loc\notin\operatorname{dom}\smsmonitor &
    \smsmonitor[']=\smsmonitor\cup\left\{(\loc,n)\right\}
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\absev{Alloc\ }\loc\ n}
  }{sms-alloc}
  %
  \typerule{sms-dealloc}{
    (\loc,n)\in\smsmonitor &
    \smsmonitor[']=\smsmonitor\setminus\left\{(\loc,n)\right\}
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\absev{Dealloc\ }\loc}
  }{sms-dealloc}
\end{center}
\begin{center}
  \judgbox{\smstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ with respect to \gls{sms}.''}$\;$\\
  %
  \typerule{sms-alloc-authentic}{
  }{
    \smstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ n}
  }{sms-alloc-authentic}
  %
  \typerule{sms-dealloc-authentic}{
  }{
    \smstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{sms-dealloc-authentic}
  %
  \typerule{sms-use-authentic}{
  }{
    \smstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc\ n}
  }{sms-use-authentic}
  %
  \typerule{sms-branch-authentic}{
  }{
    \smstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{sms-branch-authentic}
  %
  \typerule{sms-binop-authentic}{
  }{
    \smstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{sms-binop-authentic}
  %
  \typerule{sms-empty-authentic}{
  }{
    \smstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{sms-empty-authentic}
  %
  \typerule{sms-abort-authentic}{
  }{
    \smstraceagree[]{\lightning}{\absterm}
  }{sms-abort-authentic}
\end{center}

The state of the monitor for \gls{sms} is a set containing pairs of locations and the allocation size of the objects the locations point to.
In comparison to the trace model of the \gls{tms} monitor, the trace model here is extended by sizing and positional information.
\Cref{tr:sms-use} performs a bounds check and \Cref{tr:sms-alloc,tr:sms-dealloc} add or remove locations and the size of an allocation.
The trace agreement relation is, again, entirely straightforward.

\begin{lemma}[Monitor Traces are $\smssafe$]\label{lem:mon:smsafe}
  If $\monsmssafe{\trace}$, then $\trace\in\smssafe$.\Coqed
\end{lemma}

\paragraph{Comining Monitors: \glsfirst{ms}}

>>>>

Given a partial program $\progvar$, i.e., a program with free variables, the execution of $\progvar$ would get stuck due to the lack of definitions.
%As described earlier, partial programs cannot be executed \MP{not true anymore, need to define the notion of partial programs} , because they lack definitions and, thus, get stuck.
To remedy this, {\em linking} takes two partial programs $\progvar[_{1}],\progvar[_{2}]$ and produces a new whole program $\link{\progvar[_{1}]}{\progvar[_{2}]}$.
%Note that linking is not defined on programs, but merely on their syntactic descriptions, since programs contain dynamic state.\MP{ not terminology i really want to use, nor is defined}
As typically done in secure compilation~\cite{abate2019jour}, \MP{others do this too, parametricity results e.g.} this paper assumes that programs are the result of linking a {\em context} ($\ctx$) and a {\em component} ($\comp$).
% \MP{just introduce the notion of contexts}
%       MK: why only contexts?
%The component part of a whole program is the main object of interest and thus a known syntactic description.
The context is usually arbitrary\footnote{Up to, e.g., provoking link failure by giving multiple definitiions for the same name.} and thus has the role of an {\em attacker} that can interact with the component by means of whatever features the programming language has.
The semantics of the programming language is expected to differentiate between the component and the context.
%\MP{and say the semantics is expected (passive, hah) to differentiate between prg and ctx}
%%                                         -> why passive?
So, the context interacts in some way with the component and this interaction models an attacker.
With this, \Thmref{def:propsat} can be extended as follows.
For \bul{programs $\progvar$ to robustly satisfy a property $\pi$}, take an \iul{attacker $\contextvar$ and link it with $\progvar$}, \oul{the result of which must satisfy $\pi$}.
%The following definition extends on \Thmref{def:propsat} to cover property satisfaction under the presence of an (active, with respect to the semantics of the programming language) attacker: %, which is known as {\em robust satisfaction}:
%\MPin{missing: the context is an attacker! now, unlike before, we security property satisfaction with a clear active attacker}

@@

\section{Example Properties\pages{1.5}}\label{sec:compprop}

This section introduces a trace model (\Cref{subsec:propdefs}) and defines some example properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{scct}).
These properties are of practical importance and also of interest in the case study (\Cref{sec:casestud:defs,sec:casestud:rtp}) this paper presents.
\subsection{Specification Trace Model}\label{subsec:propdefs}

@@

The specification trace model defines events as either the empty event ($\emptyevent$), a crash ($\lightning$), or as tuples consisting of a pre--event, a control--tag, and a security--tag.
The purpose of the model is to define properties, such as a stricter variant of cryptographic constant time.
To this end, security--tags indicate wether an event contains sensitive information ($\lock$) or not ($\unlock$), while control--tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
The latter is necessary to be able to ignore actions done by a spurious context that, e.g., immediately deallocates a memory location twice, thus violating \gls{tms}.
%Even though this could be used for blame~\cite{patrignani2023blame}, this is not what this paper is concerned about.
Lastly, pre--events describe the actual kind of event that happened.
One such kind is the allocation event ($\ev{Alloc\ \loc\ n}$) that fires whenever a program claims $n$ cells of memory and stores them at address $\loc$.
Likewise, deallocation ($\ev{Dealloc\ \loc}$) announces that the object at location $\loc$ is freed.
These two events alone allow already a partial description of \gls{tms} by requiring that, e.g., there is only one deallocation event that carries a location $\loc$.
To be able to express \gls{sms}, there is also an event to describe reads from and writes to memory ($\ev{Use\ \loc\ n}$).
Finally, for cryptographic code, there is a general guideline that secrets must not be visible on a trace.
Moreover, an instruction whose timing is data--dependent must not have a secret as an operand.
Typical operations with data--dependent timing are branches and certain binary operations, such as division\footnote{This is highly architecture dependent, but division is an operation that serves as a classic example for a data--dependent timing instruction.}.
Both operations are also modelled in the specification trace model ($\ev{Branch\ n}$ and $\ev{Binop\ n}$).

\subsection{Temporal Memory Safety}

\gls{tms} is a safety property that describes that an unallocated object must not be used in any way.
Moreover, the property requires that all allocated objects must be deallocated at some point.

\begin{definition}[\glsfirst{tms}]\label{def:trace:tmsdef}
  $$
  \tmssafe:=\left\{\trace \left| \begin{array}{rcl}
                              \ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \ev{Use\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \text{if }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\text{ in }\trace&\text{then}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'}\text{ in }\trace \\
                              \text{at most one }\ev{Dealloc\ \loc;\sandboxtag;\securitytag}&\text{in}&\trace \\
                              \text{at most one }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\text{in}&\trace \\
                            \end{array}\right.\right\}
  $$
\end{definition}
Hereby, the notation $\event[_{1}]\le_{\trace}\event[_{2}]$ means that if $\event[_{1}]$ is in $\trace$ and if $\event[_{2}]$ is in $\trace$, then $\event[_{1}]$ appears before $\event[_{2}]$.

\subsection{Spatial Memory Safety}

\gls{sms} disregards out of bounds accesses:

\begin{definition}[\glsfirst{sms}]\label{def:trace:smsdef}
  $
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
  $
  A trace $\trace$ is spatial memory safe ($\trace\in\smssafe$) iff given $\ev{Alloc\ \loc\ m;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ n;\sandboxtag';\securitytag'}$, then $n<m$.
\end{definition}

\subsection{Memory Safety}

Full \gls{ms} is then described as the conjunction of \Cref{def:trace:tmsdef,def:trace:smsdef}.
Note, however, that this definition does not entail memory--safety issues introduced by side--channels, such as speculation.

\begin{definition}[\glsfirst{ms}]\label{def:trace:msdef}
  $
  \mssafe:=\left\{\trace \left|\begin{array}{rcl}
                                 \trace\in\tmssafe & \text{ and } & \trace\in\smssafe
                               \end{array}\right.\right\}
  $
  A trace $\trace$ is memory safe ($\trace\in\mssafe$) iff $\trace\in\tmssafe$ and $\trace\in\smssafe$.
\end{definition}

\subsection{Strict Cryptographic Constant Time}

\gls{cct} is a hyperproperty and, thus, not as easy to check with just monitors. %Beutner et al
Hence, the following defines \gls{scct}, a stricter variant that enforces the policy that no secret should appear on a trace.

\begin{definition}[\glsfirst{scct}]\label{def:trace:scctdef}
  $
  \scctsafe:=\left\{\trace \left|\begin{array}{rcl}
                                   \trace=\hole{\cdot} & \text{ or } & \trace=\event[_{b}];\sandboxtag;\unlock\cdot\trace['] \wedge \trace[']\in\scctsafe
                                 \end{array}\right.\right\}
  $
\end{definition}

\subsection{Memory Safe, Strict Cryptographic Constant Time}

The combination of \gls{ms} and \gls{scct} is the intersection of these properties, \gls{msscct}.
It entails all program behaviours that are both memory safe and strictly cryptographic constant time.

\begin{definition}[\glsfirst{ms} and \gls{scct}]\label{def:trace:msscctdef}
  $
  \msscctsafe:=\left\{\trace \left| \begin{array}{rcl}
                                      \trace\in\mssafe & \text{ and } & \trace\in\scctsafe
                                    \end{array}\right.\right\}
  $
\end{definition}

%\section{Monitors and Trace Agreements\pages{1.5}}\label{sec:monitors}
\section{Monitors\pages{1.5}}\label{sec:monitors}
This section introduces monitors for each of the properties presented earlier (\Cref{subsec:propdefs}).
The use of monitors is because they have some structure useful for inductive proofs, whereas traces lack this structure, thus making proofs difficult.
To lessen the burden when proving, each monitor makes use of a custom trace model that contains only the relevant information related to the property the monitor checks.
To project specification traces $\trace$ onto these monitor--level traces $\abstrace$, each property has an associated event agreement relation $\traceagree[]{\pi}{\trace}{\abstrace}$.
This relation performs the actual work of projecting the events, while the stutter--equivalence $\traceagree{\pi}{\trace}{\abstrace}$ remains the same for all properties $\pi$, yet is indexed by $\pi$ to emphasize the kind of event agreement.
With agreements, this section starts to define monitor satisfaction for traces and states that monitor satisfaction implies property satisfaction.
To this end, monitor satisfaction is defined as follows.
\bul{A specification trace $\trace$ monitor--satisfies property $\pi$} iff there exists a (final) monitor state $\monitor$ and an abstract trace $\abstrace$ such that the \iul{specification trace $\trace$ agrees with abstract trace $\abstrace$} and \oul{the initial monitor\footnote{In this paper, for all monitors, the initial monitor state is denoted as $\emptyset$.} can step to the (final) monitor state $\monitor$ with abstract trace $\abstrace$}.

\begin{definition}[Monitor Satisfaction]\label{def:monsat}
  \bul{$\monsafe{\trace}{\pi}$} iff $\exists \abstrace\ \monitor$ such that \iul{$\traceagree{\pi}{\trace}{\abstrace}$} and \oul{$\monitorcheck{\emptyset}{\monitor}{\abstrace}$}.
\end{definition}

\subsection{Monitor for \glsfirst{tms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{allocated}:L\times\sandboxtag,\text{freed}:L\times\sandboxtag\right\} \hspace{0.33cm}%
    \emptyset:=\ \left\{\text{allocated}:\emptyset,\text{freed}:\emptyset\right\}\\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ does one step to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
  \typerule{tms-uninteresting}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
  }{tms-uninteresting}
  %
  \typerule{tms-abort}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
  }{tms-abort}
  %
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{allocated}: \tmsmonitor.\text{allocated}\cup\left\{(\loc;\sandboxtag)\right\},\text{freed}: \tmsmonitor.\text{freed}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{allocated}: \tmsmonitor.\text{allocated}\setminus\left\{(\loc;\sandboxtag)\right\},\text{freed}: \tmsmonitor.\text{freed}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
\end{center}

The state of the monitor is a record with two sets keeping track of allocated and deallocated locations.
%The monitor runs on a modified trace semantics with more abstract $\absev{Alloc\ }\loc$,$\absev{Dealloc\ }\loc$,$\absev{Use\ }\loc$, and $\absterm$ events, which represent {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.
\Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
\Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and extend the monitor state accordingly.
This restriction effectively disallows reallocation to reassign the same location to an object.
However, the definition can easily be adapted by, e.g., attaching a natural number serving as a counter.
In the reflexive case of $\monitorcheck{\tmsmonitor}{\tmsmonitor}{\absevent}$, the monitor $\tmsmonitor$ must not contain allocated locations, i.e., $\tmsmonitor.allocated=\emptyset$.
This ensures that programs do not forget to free memory.

\begin{center}
  \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ with respect to \gls{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc-authentic}
  %
% \typerule{tms-dealloc-authentic}{
% }{
%   \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
% }{tms-dealloc-authentic}
  %
% \typerule{tms-use-authentic}{
% }{
%   \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
% }{tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{tms-branch-authentic}
  %
% \typerule{tms-binop-authentic}{
% }{
%   \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
% }{tms-binop-authentic}
% %
% \typerule{tms-empty-authentic}{
% }{
%   \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
% }{tms-empty-authentic}
% %
  \typerule{tms-abort-authentic}{
  }{
    \tmstraceagree[]{\lightning}{\absterm}
  }{tms-abort-authentic}
\end{center}

The trace agreement is entirely straightforward, so only allocation, branch, and crash are shown.

\begin{lemma}[Traces with Monitor Satisfaction are $\tmssafe$]\label{lem:mon:tmsafe}
  If $\montmssafe{\trace}$, then $\trace\in\tmssafe$. %\Coqed
\end{lemma}
